Automated topic naming to support analysis of software maintenance activities

### 2010-08-19 icse/icse2011.tex
More edits

@@

Topics in software engineering practice refer to specific `threads' between project stakeholders. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
In addressing a topic of development stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.
The goal of concept location and topic analysis research is to recover these topics and the related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not globally generalizable.
% get the interpretation aspect
Much of the current research stops short of interpreting the purpose of the topic. That is, extracted topics are usually manually named and labelled by those who read the topic words.
% 
In this paper we propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

% topics are numerous?
Deriving such topics is difficult. 
Raw topics from topic analysis are represented as unlabelled context-free word-lists or word distributions.
Topics have to be identified by interpreting the prevalent words in a word distribution and by inspecting related documents. 
This manual approach is impractical when one has to handle hundreds of different topics; to scale to meaningfully sized projects, we require automatic assistance to determine the topic label.

% why are topics useful
Often developers interact with abstractions of these artifacts that topics are derived from, rather than the artifact itself. 
Topics are a valuable and automatically extractable abstraction of software artifacts.
It abstracts these artifacts by their purpose or topic rather than their concrete representation.
The topic of development is relevant because it shows anyone inspecting these topics what are the distinct issues or topics facing development at a certain time.
Such abstractions include project dashboards~\cite{kersten2005mylar}, tags~\cite{treude2010}, and complexity metrics \cite{mccabe1976complexity}.

@@

\section{Study design and execution}
Figure \ref{fig:process} gives an outline of the methodology followed. We began by gathering source data; then applied unsupervised and supervised learning techniques to identify topics. We then use these topics to analyze the role of non-functional requirements in software maintenance.

>>>>

% Maybe specify the hard work we did annotating the data

@@

Topics in software engineering practice refer to specific `threads' between project stakeholders. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
While addressing a topic of development, stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics can be in several potential states: they may not be immediately resolved, they may re-occur, yet other topics may be only dealt with briefly, such as a  bug report that is closed.
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.
The goal of concept location and topic analysis research is to recover these topics and their related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not globally generalizable.
% get the interpretation aspect
Much of the current research stops short of interpreting the purpose of the topic. That is, extracted topics are usually manually named and labelled by those who read the topic words.
% 
In this paper we propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

% topics are numerous?
Deriving such topics is difficult. 
Topic analysis produces raw topics that are represented as unlabelled context-free word-lists or word distributions.
Topics have to be identified by interpreting the prevalent words in a word distribution and by inspecting related documents. 
This manual approach is impractical when one has to handle hundreds of different topics; to scale to meaningfully sized projects, we require automatic assistance to determine the topic label.

% why are topics useful
Often developers interact with abstractions of these artifacts that topics are derived from, rather than the artifact itself. 
Topics are a valuable and automatically extractable abstraction of software artifacts.
These artifacts are abstracted by their purpose or topic rather than their concrete representation.
The topic of development is relevant because it shows anyone inspecting these topics what are the distinct issues or topics facing development at a certain time.
Other such abstractions include project dashboards~\cite{kersten2005mylar}, tags~\cite{treude2010}, and complexity metrics \cite{mccabe1976complexity}.

@@

\todo[inline]{We still haven't shown that topics are useful -- a reviewer comment}

\section{Study design and execution}
Figure \ref{fig:process} gives an outline of the methodology followed. We began by gathering source data;
then we manually annotated the topics of these sources by their related NFRs;
 then applied unsupervised and supervised learning techniques to identify topics. We then use these topics to analyze the role of non-functional requirements in software maintenance.
